No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido

### 2022-06-01 paper/paper_draft.Rmd
knit

```{r read, include=FALSE, eval=TRUE}
library(readr)
sort_read_count <- read.csv("~/Downloads/sort.read_count.txt", header = FALSE)
# View(sort_read_count)
sort_read_count <- sum(sort_read_count$V1)

sort_flt_read_count <- read.csv("~/Downloads/sort.flt.read_count.txt", header = FALSE)
# View(sort_flt_read_count)
sort_flt_read_count <- sum(sort_flt_read_count$V1)

>>>>

```{r read, include=FALSE, eval=TRUE}
library(readr)
sort_read_count <- read.csv("../sort.read_count.txt", header = FALSE)
# View(sort_read_count)
sort_read_count <- sum(sort_read_count$V1)

sort_flt_read_count <- read.csv("../sort.flt.read_count.txt", header = FALSE)
# View(sort_flt_read_count)
sort_flt_read_count <- sum(sort_flt_read_count$V1)
